Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-07-17 manuscript.tex
5.3 updates

For each of the 4500 simulations we derived at first the corresponding three set of RV, namely N mean RV, SN mean RV and SN median RV. 
On each of those RV sets, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
or the usual correction along with a circular planetary signal (see Eq.~\eqref{eq:RV:correction.overall}). Because of the non-linearity of the model to account for the
planet, we used a non-linear least squares for the fit \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear}. Such a model requires
initial conditions close to the real solution, otherwise the algorithm can converge to a local minimum. Because our goal here is to compare the planetary detection limits
using the three different RV estimates and the two different activity model proposed, and not to discuss what is the best method to explore the parameter space, we 
initialised the minimisation algorithm to the real period of the planetary signal injected to avoid to get stuck in a local minimum. We also selected as initial amplitude the peak-to-peak amplitude of the RV data set.
The argument of periapsis $t_0$ was initialised to the time when the RV were crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).

@@

Once the parameters involved in Eq.~\eqref{eq:RV:correction.overall} have been estimated,  signals in the residuals, defined as $RV - RV_{\text{activity}}$, were analyzed using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}. 
If a signal with a P-value\footnote{The P-values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.  
For each period considered, we searched for the minimum amplitude at which at least 80\% of the planets with different phases were detected.
This minimum amplitude detected as a function of period is shown in Fig.~\ref{fig:detection_limits} for the three different RV estimates (N mean RV, SN mean RV, and SN median RV) when using the new stellar activity correction proposed in this paper (see Eq.~\eqref{eq:RV:correction}), and when using the usual activity correction.
We can see that the new correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves by 12\% on average the detection limit of the exoplanet compared to the usual approach, and the three estimators of RV give similar detection limits.
These results therefore suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity, and using our new model to account for stellar activity allows to detect planetary signals with a slightly smaller amplitude that the usual correction using only a linear correlation with the FWHM and BIS SPAN.

\begin{figure}[!h]
\begin{center}
\includegraphics[height = 2.6in]{detection_limits.pdf} 
   \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in Eq.~\eqref{eq:RV:correction} (solid lines) or the usual correction based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit (dashed lines). The correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves by 12\% on average the detection limit and the different RV estimators have similar detection limits.}
   \label{fig:detection_limits}
\end{center}
\end{figure}

>>>>

For each of the 4500 simulations we computed the three estimates of RV, namely N mean RV, SN mean RV and SN median RV. 
On each set of RV estimates, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
or the usual correction along with a circular planetary signal (see Eq.~\eqref{eq:RV:correction.overall}). Because of the non-linearity of the model that includes a 
planet, a non-linear least squares algorithm was used for the fit \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear}. Such a model requires
initial conditions close to the real solution, otherwise the algorithm can converge to a local minimum. Because our goal here is to compare the planetary detection limits
using the three different RV estimates and the two different activity model proposed, and not to discuss what is the best method to explore the parameter space, we 
initialised the minimisation algorithm to the real period of the planetary signal injected to avoid getting stuck in a local minimum. We also selected as initial amplitude the peak-to-peak amplitude of the estimated RVs.
The argument of periapsis $t_0$ was initialised to the time when the RV were crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).

@@

Once the parameters involved in Eq.~\eqref{eq:RV:correction.overall} were estimated,  signals in the residuals, defined as $RV - RV_{\text{activity}}$, were analyzed using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}. 
If a signal with a P-value\footnote{The P-values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.  
For each period considered, we searched for the minimum amplitude at which at least 80\% of the planets with different phases were detected.
This minimum amplitude detected as a function of period is shown in Fig.~\ref{fig:detection_limits} for the three different RV estimates (N mean RV, SN mean RV, and SN median RV) when using the new stellar activity correction proposed in this paper (see Eq.~\eqref{eq:RV:correction}), and when using the usual activity correction.
We can see that the new correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves the detection limit of the exoplanet by 12\% on average compared to the usual approach, and the three estimators of RV give similar detection limits.
These results therefore suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity, and using our new model to account for stellar activity allows to detect planetary signals with a slightly smaller amplitude that the usual correction using only a linear correlation with the FWHM and BIS SPAN.

\begin{figure}[!h]
\begin{center}
\includegraphics[height = 2.6in]{detection_limits.pdf} 
   \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in Eq.~\eqref{eq:RV:correction} (solid lines) or the usual correction based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit (dashed lines). The correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves the detection limit by 12\% on average and the different RV estimators have similar detection limits.}
   \label{fig:detection_limits}
\end{center}
\end{figure}
